Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-02-03 paper/elsarticle/main.tex
Review: Sec.3

	For a better insight into the proposed technique, the procedure of self-tuning is depicted in Fig.~\ref{fig:tuning}.

	\begin{figure}
		\begin{center}
			\includegraphics[width=\textwidth]{images/tuning}
			\caption[Self-tuning scheme]{Self-tuning scheme.}
			\label{fig:tuning}
		\end{center}
	\end{figure}

>>>>

	For a detailed insight into the proposed control technique, the procedure of self-tuning evaluation is depicted in Figure~\ref{fig:tuning}.

	\begin{figure}
		\begin{center}
			\includegraphics[width=\textwidth]{images/tuning}
			\caption[Self-tuning scheme]{Scheme of the self-tuning control evaluation.}
			\label{fig:tuning}
		\end{center}
	\end{figure}
